A user-extensible and adaptable parser architecture

### 2008-05-30 papers/sgai-2008/paper.tex
Wrote the conclusion. Added a little to the introduction.

\newcommand{\numberOFrulesMINIMUM}[0]{%
    119 XXX CHECK THIS NUMBER%
}

% \numberOFrulesMINIMUM as percentage of \numberOFrules
\newcommand{\numberOFrulesMINIMUMpercentage}[0]{%
    70.41\%%
}

% \numberOFrules as percentage increase of \numberOFrulesMINIMUM
\newcommand{\numberOFrulesMAXIMUMpercentage}[0]{%
    42.01\%%
}

@@

@@

XXX WRITE THE CONCLUSION\@.

Makes adding new rules trivial, new actions tractable.  Knowledge of the
framework is rarely necessary.

The architecture's greatest strength is the ease with which new inputs can
be parsed and new actions written.

System could be used by mail administrators to monitor restrictions.

Explain how someone could build upon it, e.g.\ to parse further Postfix
stuff, or to parse other logs entirely.

``This is a real world application, based on a real world need, rather than
a toy application built as a proof of concept''  Put this in the
introduction as well.

>>>>

\newcommand{\numberOFrulesMINIMUM}[0]{%
    115%
}

% XXX FIGURE OUT HOW TO DO THIS AUTOMATICALLY
% \numberOFrulesMINIMUM as percentage of \numberOFrules
\newcommand{\numberOFrulesMINIMUMpercentage}[0]{%
    68.04\%%
}

% \numberOFrules as percentage increase of \numberOFrulesMINIMUM
\newcommand{\numberOFrulesMAXIMUMpercentage}[0]{%
    46.95\%%
}

@@

This architecture is ideally suited to parsing inputs where the input is
not fully understood or does not follow a fixed grammar: the architecture
warns about unparsed inputs and other errors, but continues on parsing as
best it can, allowing the developer of a new parser to decide which
deficiencies are most important and require attention first, rather than
being forced to fix the first error which arises.

@@

The architecture's greatest strength is the ease with which is can be
adapted to deal with new requirements and inputs.  Parsing a variation of
an existing input is a trivial task: simply modify an existing rule or add
a new one with an appropriate \regex{} and the task is complete; knowledge
of the framework is not required when writing rules.  Parsing a new
category of input is achieved by writing a new action and appropriate
rules; quite often the action will not need to interact directly with
existing actions, but when interaction is required the framework provides
the necessary facilities.  The decoupling of rules from actions allows
different sets of rules to be used with the same actions: e.g.\ a parser
might have actions to process versions one and two of a file format; the
parser will then parse either version one or version two depending on the
ruleset selected.  The architecture makes it possible to apply commonly
used programming techniques such as object orientation, inheritance,
composition, delegation and roles when designing and implementing a parser,
simplifying the process of working within a team with shared responsibility
or developing and testing additional functionality.

Developing a new parser based on this architecture follows a similar
process to developing a new parser using any architecture: study the
inputs, figure out what needs to happen for each category of input
(actions), and write a specification identifying each type of input
(rules); the existing framework should be suitable for use with the
majority of parsers.  If the inputs to be parsed are suitable a large
amount of work can be done with very little effort by using \SLCT{} to
identify similar lines in the input and generate \regexes{} to match those
lines; these \regexes{} will form the basis of the initial ruleset.  When
the commonly occurring inputs are parsed by rules and actions, the process
of identifying and rectifying parsing deficiencies can begin, with each
iteration of the development process improving the parser, similar to
Stepwise Refinement~\cite{stepwise-refinement}.

XXX PUT THIS IN THE INTRODUCTION AS WELL\@.  The Postfix log file parser
based on this architecture provides a basis for systems administrators to
monitor the effectiveness of their anti-spam measures and adapt their
defences to combat the new techniques used by those sending spam.  The
parser is a fully usable application, built to address a genuine need,
rather than a proof of concept whose sole purpose is to illustrate a new
idea; it deals with the oddities and difficulties which occur in the real
world, rather than a clean, idealised scenario developed to showcase the
best features of a new approach.
